An Improved ANS Transaction Template

### 2018-01-25 paper.tex
fix the flow

As it is practically impossible to get reliable information about tuning a
cascade when feed with a different feed assay than the one used for its design.
Two different tuning have been considered, the first one makes the hypothesis
that no physical change are made to the different centrifuges: the cut on the
machine remains the same at every stage. The second considered tuning option,
keep the enrichment factor constant implying to modify the cuts and then the
different flows.

The first tuning method assumes the cut of each stages are constant. As $\delta
U$ and $\alpha$ do not depend on the stage feed assay $N'$,the feed to product
ratio $\alpha$ do not change across the different stages. According to equation
\eqref{eq:beta} , when $\alpha$ and $\theta$ remaining, if the feed assay,
$N$, change $\beta$ has to change accordingly.  This will lead to brake of the
ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.

@@

\subsection{Case 1}
\subsection{Case 2}

>>>>

As it is practically impossible to get reliable information about tuning a
cascade when feed with a different feed assay than the one used for its design.
Hypothesis have been made to design the response of the cascade: no physical
change are made to the different centrifuges: the cut on the machine remains the
same at every stage.

This tuning method assumes the cut of each stages are constant. As $\delta
U$ and $\alpha$ do not depend on the stage feed assay $N'$,the feed to product
ratio $\alpha$ do not change across the different stages. According to equation
\eqref{eq:beta} , when $\alpha$ and $\theta$ remaining, if the feed assay,
$N$, change $\beta$ has to change accordingly.  This will lead to brake of the
ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.

@@

\subsection{Case 1}
The case 1 is design to allow configure 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. The design properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.035/0.003.\\
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0412842/0.00290548.\\

\subsection{Case 2}
